Status of nuclear optical potentials and future prospects

### 2019-07-09 Notes/Candidacy/Paper/candidacy_paper.tex
Update candidacy_paper.tex

Things to include:
\\
-- Why are nuclear reactions important? (Processes that help us understand nuclear structure amongst other things.) List examples.
\\
-- r-process for motivation.
\\
-- How do optical potentials help us understand nuclear reactions?
\\
-- References: ...

@@

Things to include:
\\
-- More general things from Thompson/Nunes: define optical potentials as complex potentials and consequences of this. Reaction cross section derivation.
\\
-- Derivation of the general optical potential (equation (2.15) in Feshbach).
\\
-- Properties of the potential: complex (meaning), non-local (derivation), dispersion relation.
\\
-- Relation to observables (basic quantum stuff?)
\\
-- References: \cite{Feshbach:1958nx}, \cite{Feshbach:1962ut}, \cite{thompson_nunes_2009}.

@@

Things to include:
\\
-- Successes and limitations.
\\
-- Motivation: predictions for exotic region of the nuclear chart.
\\
-- Major methods: Multiple scattering (see references in Dickhoff paper) and Green's function based methods (coupled cluster).
\\
-- Coupled cluster Green's function \cite{Rotureau:2016jpf}.
\\
-- References: \cite{Dickhoff:2018wdd} section 4, \cite{Furumoto:2019anr} G-matrix interaction, \cite{Idini:2019hkq} self-consistent Green's function, \cite{Rotureau:2016jpf}.

>>>>

Things to include:
\\
-- Why are nuclear reactions important? (Processes that help us understand nuclear structure amongst other things. Exotic nuclei are short-lived and must used reactions to study them.) List examples.
\\
-- r-process for motivation.
\\
-- How do optical potentials help us understand nuclear reactions?
\\
-- References: ...

@@

Things to include:
\\
-- More general things from Thompson/Nunes: define optical potentials as complex potentials and consequences of this. Reaction cross section derivation.
\\
-- Derivation of the general optical potential (equation (2.15) in Feshbach).
\\
-- Relation to observables (basic quantum stuff?)
\\
-- Derivation with projection operators.
\\
-- References: \cite{Feshbach:1958nx}, \cite{Feshbach:1962ut}, \cite{thompson_nunes_2009}.

@@

Things to include:
\\
-- Successes and limitations.
\\
-- Motivation: predictions for exotic region of the nuclear chart.
\\
-- Major methods: Multiple scattering (see references in Dickhoff paper) and Green's function based methods (coupled cluster). SRG evolution.
\\
-- Coupled cluster Green's function \cite{Rotureau:2016jpf}.
\\
-- References: \cite{Dickhoff:2018wdd} section 4, \cite{Furumoto:2019anr} G-matrix interaction, \cite{Idini:2019hkq} self-consistent Green's function, \cite{Rotureau:2016jpf}.
